---
title: "Assignment 9"
author: "Prashant Gupta"
Vid: "V01038654"
output: html_document
---

```{r warning=FALSE}
library(forecast)

```



### Loading The Data
```{r}
shampoo.df <- read.csv("ShampooSales.csv")
shampoo.ts <- ts(shampoo.df$Shampoo.Sales, 
                   start = c(1995, 1), end = c(1997, 12), freq = 12)
```


### Splitting the data into training and validation, keeping the last 3 months for validation.

```{r}

nValid <- 3
nTrain <- length(shampoo.ts) - nValid
train.ts <- window(shampoo.ts, start = c(1995, 1), end = c(1995, nTrain))
valid.ts <- window(shampoo.ts, start = c(1995, nTrain + 1), 
                   end = c(1995, nTrain + nValid))
```


### Fitting an exponential smoothing model

```{r}
plot(train.ts, xlab = "Time", ylab = "Shampoo Sales", bty = "l")
```
#### We can see that there is Upward Exponantial Trend with additive Seasonality.

```{r}
seasonplot(train.ts, ylab="Shampoo Sales", 
           xlab="Year", main="Seasonal Plot", year.labels=TRUE)
```


```{r}
monthplot(train.ts, ylab="Shampoo Sales", 
          xlab="Year", main="Seasonal Deviation Plot")
```

#### We can jee that either people but more shampoo July-Aug or they but at Sep- Nov


### What ETS() model would you recommend for this data?
```{r}
ETS.model1 <- ets(train.ts, model = "AMA", restrict=FALSE) # Additive error, multiplicative trend, additive season
ETS.model1
```



```{r}
ETS.model2 <- ets(train.ts, model = "AMN", restrict=FALSE) # Additive error, multiplicative trend, no season
ETS.model2
```

```{r}
ETS.model3 <- ets(train.ts, model = "AAA", restrict=FALSE) # Additive error, additive trend, additive season
ETS.model3
```

```{r}
ETS.model4 <- ets(train.ts, model = "AAN", restrict=FALSE) # Additive error, additive trend, no season
ETS.model4
```

```{r}
ETS.model5 <- ets(train.ts, model = "MMA", restrict=FALSE) # Multiplicative error, multiplicative trend, additive season
ETS.model5
```

```{r}
ETS.model6 <- ets(train.ts, model = "MMN", restrict=FALSE) # Multiplicative error, multiplicative trend, no season
ETS.model6
```

```{r}
ETS.model7 <- ets(train.ts, model = "MAA", restrict=FALSE) # Multiplicative error, additive trend, additive season
ETS.model7
```

```{r}
ETS.model8 <- ets(train.ts, model = "MAN", restrict=FALSE) # Multiplicative error, additive trend, no season
ETS.model8

```

```{r}
ETS.alg.model <- ets(train.ts, restrict = FALSE)
ETS.alg.model
```

```{r}
ETS.model2.pred <- forecast(ETS.model2, h = nValid)
ETS.alg.model.pred <- forecast(ETS.alg.model, h = nValid)
```

### Fit an ARIMA model

```{r}
tsdisplay(train.ts)
```

### What level of differencing do you need?

```{r}
diff1.train.ts <- diff(train.ts, lag = 1)
tsdisplay(diff1.train.ts)
```

```{r}
diff2.train.ts <- diff(train.ts, lag = 2)
tsdisplay(diff2.train.ts)
```

```{r}
diff12.train.ts <- diff(train.ts, lag = 12)
tsdisplay(diff12.train.ts)
```

```{r}
ndiffs(train.ts)
```

```{r}
nsdiffs(train.ts)
```

### Create an ACF and PACF plot on the differenced data.

```{r}

tsdisplay(diff1.train.ts)
```

# Fit your recommended ARIMA model.

```{r}
ARIMA.model1 <- Arima(train.ts, order = c(1,1,0), seasonal=c(0,0,0))
summary(ARIMA.model1)
```

```{r}
ARIMA.model2 <- Arima(train.ts, order = c(0,1,1), seasonal=c(0,0,0))
summary(ARIMA.model2)
```

```{r}
ARIMA.model3 <- Arima(train.ts, order = c(1,1,1), seasonal=c(0,0,0))
summary(ARIMA.model3)
```

```{r}
ARIMA.alg.model <- auto.arima(train.ts)
summary(ARIMA.alg.model)
```

```{r}
ARIMA.model1.pred <- forecast(ARIMA.model1, h = nValid)
ARIMA.alg.pred <- forecast(ARIMA.alg.model, h = nValid)
```

### Assess the predictive accuracy of your ETS and ARIMA models in cross-validation?


```{r}
accuracy(ETS.model2.pred, valid.ts)
accuracy(ETS.alg.model.pred, valid.ts)
accuracy(ARIMA.model1.pred, valid.ts)
accuracy(ARIMA.alg.pred, valid.ts)
```

