---
title: "Assignment 8 "
author: "Prashant Gupta"
Vid: "V01038654"
output: html_document
---
```{r message=FALSE, warning=FALSE}
library(forecast)

```

### Laoding the Data

```{r}
wine.data = read.csv('AustralianWines.csv')

```


```{r}
wine.ts <- ts(wine.data$Fortified, 
                   start = c(1980, 1), end = c(1993, 12), freq = 12)
```

```{r}
nValid <- 36
nTrain <- length(wine.ts) - nValid

# partition the data
train.ts <- window(wine.ts, start = c(1980, 1), end = c(1980, nTrain))
valid.ts <- window(wine.ts, start = c(1980, nTrain + 1), 
                   end = c(1980, nTrain + nValid))
```

```{r}

plot(train.ts, xlab = "Time", ylab = "Fortified Wine")
```

### 1. Fit a regression model to the training data with a linear trend and additive seasonality.

```{r}
train.lm.trend.season <- tslm(train.ts ~ trend + season)
summary(train.lm.trend.season)
train.lm.trend.season.pred <- forecast(train.lm.trend.season, h = nValid)
```

```{r}
plot(train.ts, ylab = "Fortified Wine", xlab = "Time", bty = "l", 
     xlim = c(1980,1993), main = "")
lines(train.lm.trend.season.pred$fitted, lwd = 2, col = "blue", lty = 3)
lines(train.lm.trend.season.pred$mean, lwd = 2, col = "blue", lty = 3)
lines(valid.ts, col = "grey20", lty = 3)
```

### Forecast

```{r}
plot(train.lm.trend.season.pred, ylab = "Fortified Wine", xlab = "Time", bty = "l", 
     xlim = c(1980,1993), main = "")
```

### 2.Fit an ARIMA model

#### What level of differencing do you need?
```{r}
ndiffs(train.ts)


nsdiffs(train.ts)

```
### So d = 1 D = 1, 

### Create an ACF and PACF plot on the differenced data.

```{r}

double.diff.train.ts <- diff(diff(train.ts, 1), 12)
tsdisplay(double.diff.train.ts)
```

#### We can try any of p = 1 or q = 1 and P = 1 or Q = 1


### What AR and MA terms do you need?
```{r}
ARIMA1.fit <- Arima(train.ts, order = c(1,1,0), seasonal=c(1,1,0))
summary(ARIMA1.fit)
```

```{r}
ARIMA2.fit <- Arima(train.ts, order = c(0,1,1), seasonal=c(1,1,0))
summary(ARIMA2.fit)
```

```{r}
ARIMA3.fit <- Arima(train.ts, order = c(1,1,0), seasonal=c(0,1,1))
summary(ARIMA3.fit)
```

```{r}
ARIMA4.fit <- Arima(train.ts, order = c(0,1,1), seasonal=c(0,1,1))
summary(ARIMA4.fit)
```

### What ARIMA model would you recommend for this data? (If you are unsure then try several)


#### p = 0, d = 1, q = 1, P = 0, D = 1, Q = 1

### Fit your recommended ARIMA model

```{r}
man.ARIMA.fit <- Arima(train.ts, order = c(0,1,1), seasonal=c(0,1,1))
summary(man.ARIMA.fit)
```

```{r}
man.ARIMA.pred <- forecast(man.ARIMA.fit, h = nValid)
```

### Create a plot to compare the fit to the training and validation set.

```{r}
plot(train.ts, ylab = "Fortified Wine", xlab = "Time", bty = "l", 
     xlim = c(1980,1993), main = "")
lines(man.ARIMA.pred$fitted, lwd = 2, col = "blue", lty = 3)
lines(man.ARIMA.pred$mean, lwd = 2, col = "blue", lty = 3)
lines(valid.ts, col = "grey20", lty = 3)
```

### Create a plot to show the forecast and prediction interval.

```{r}
plot(man.ARIMA.pred, ylab = "Fortified Wine", xlab = "Time", bty = "l", 
     xlim = c(1980,1993), main = "")
```

### 3.Use auto.arima() to fit an ARIMA (p, d, q) (P, D, Q) model to the training data

```{r}
auto.ARIMA.fit <- auto.arima(train.ts)
summary(auto.ARIMA.fit) 
```

```{r}
auto.ARIMA.pred <- forecast(auto.ARIMA.fit, h = nValid)
```


### Create a plot to compare the fit to the training and validation set.
```{r}
plot(train.ts, ylab = "Fortified Wine", xlab = "Time", bty = "l", 
     xlim = c(1980,1993), main = "")
lines(auto.ARIMA.pred$fitted, lwd = 2, col = "blue", lty = 3)
lines(auto.ARIMA.pred$mean, lwd = 2, col = "blue", lty = 3)
lines(valid.ts, col = "grey20", lty = 3)
```

### Create a plot to show the forecast and prediction interval.

```{r}
plot(auto.ARIMA.pred, ylab = "Fortified Wine", xlab = "Time", bty = "l", 
     xlim = c(1980,1993), main = "")
```

### 4.Which model predicts the validation data most accurately?
```{r}
accuracy(train.lm.trend.season.pred, valid.ts)

```
```{r}
accuracy(man.ARIMA.pred, valid.ts)

```

```{r}

accuracy(auto.ARIMA.pred, valid.ts)
```

#### auto.ARIMA model is the best because it's RMSE better overall.