---
title: "Assignment 6 "
author: "Prashant Gupta"
Vid: "V01038654"
output: html_document
---

```{r}
library(forecast)
library(ggplot2)
toys<-read.csv("ToysRUsRevenues.csv", stringsAsFactors = FALSE)
str(toys)
```

```{r}
head(toys)
```

```{r}
#Create a time series object out of it
toysTS <- ts(toys$Revenue, start=c(1992, 1),frequency=4)

yrange = range(toysTS)

#set up the plot
plot(c(1992,1995), yrange, type="n",xlab="Year", ylab="Revenue(millions)", bty="l", xaxt="n",yaxt="n")

#Add the time series air
lines(toysTS, bty="l")

#add the x-axis
axis(1, at=seq(1992,1995,1), labels=format(seq(1992,1995,1)))

#add the y-axis
axis(2, at=seq(1000,4500,500), labels=format(seq(1,4.5,.5)), las=2)
```

```{r}
ToysTrain<-window(toysTS,1992,c(1995,2))
ToysTrain
```


```{r}
toysLinearSeason <- tslm(ToysTrain~trend+season)
summary(toysLinearSeason)
```

```{r}
#time series object
toys.ts <- ts(toys$Revenue.in.million..., start=c(1,1), freq=4)
yrange=range(toys.ts)

#autoplotting
autoplot(toys.ts)
```

```{r}
validLength<-4
trainLength<-length(toys.ts)-validLength
trainLength
```

```{r}
SalesTrain<-window(toys.ts,end=c(1,trainLength))
SalesValid<-window(toys.ts,start=c(1,trainLength+1))
SalesTrain
```

```{r}
SalesValid
```

```{r}
#call it modelB (as in 5b) and have the dependent variable transformed
modelB<-tslm(log(SalesTrain) ~ trend + season)
summary(modelB)
```

```{r}
# use the named coefficients
q21Forecast <- modelB$coefficients["(Intercept)"] + modelB$coefficients["trend"]*21

q22Forecast <- modelB$coefficients["(Intercept)"] + modelB$coefficients["trend"]*22 + modelB$coefficients["season2"]

#convert them back and simpy echo them
exp(q21Forecast)
```

```{r}
exp(q22Forecast)
```

```{r}
#Helps set up the plot
yrange = range(toys.ts)

#set up the plot

plot(c(1,6),c(yrange[1],yrange[2]),type="n",xlab="Year", ylab="Department Sales", bty="l",xaxt="n",yaxt="n")

#add the time series air
lines(toys.ts, bty="l")

#add the x-axis
axis(1, at=seq(1,6,1), labels=format(seq(1,6,1)))
#add the y-axis
axis(2, at=seq(45000,105000,5000), labels=format(seq(45,105,5.0)), las=2)

#add the y-axis

lines(exp(modelB$fitted), col="red")
```

```{r}
forecasterror<-toys.ts-exp(modelB$fitted)
autoplot(forecasterror)
```

#### - Which two statistics (and their values) measure how well this model fits the training data?
#####   The t-value of 0.352 for the season2 variable is a measure of how many standard deviations our coefficient estimate is far away from zero.
##### The p-value for trend 9.24e-16


#### - After adjusting for trend, what is the average difference between sales in Q3 and sales in Q1?
##### Quarter 3 has a coefficient of 89.17 which is the difference between it sales and the base sales which is Quarter1.


#### - Which quarter (Q1, Q2, Q3, or Q4) has the highest average sales?
##### Quarter 4 with a coefficient of 0.976415 has the highest average sales.