---
title: "Assignment 6 "
author: "Prashant Gupta"
Vid: "V01038654"
output: html_document
---
```{r}
library(fastDummies)
library(rpart)
library(caret)
library(adabag)
library(dplyr)
```


```{r}
ebay <- read.csv("eBayAuctions.csv", stringsAsFactors = FALSE)
head(ebay)
```

### A.Fit a classification tree using all predictors, using the best-pruned tree using 5-fold cross validation.

```{r}
ebay= ebay[,-1]
data_dummies = dummy_cols(ebay, remove_first_dummy = TRUE, select_columns =colnames(select_if(ebay, is.character)), remove_selected_columns = TRUE)
data_dummies$Competitive.= as.factor(data_dummies$Competitive.)
head(data_dummies)
```

```{r}
n = nrow(data_dummies)
set.seed(101)
trainIndex = sample(1:n, size = round(0.7*n), replace=FALSE)
train = data_dummies[trainIndex ,]
test = data_dummies[-trainIndex ,]

fit = rpart(Competitive. ~., data = train)
printcp(fit)
```

```{r}
fit.pruned = prune(fit, cp = 0.010000)
pred <- predict(fit.pruned, test[,-5],type = "class")
confusionMatrix(table(test$Competitive.,pred))
```

```{r}
ebay_boosting= boosting(Competitive. ~., data=train)
pred = predict(ebay_boosting, test)
print(pred$confusion)
```


### B.Is this model practical for predicting the outcome of a new auction?
#### I think this model can be used for predicting outcome of new auction.



### D.Examine the confusion matrix for the tree on the training and validation data. What can you say about the predictive performance of this model?
```{r}
confusionMatrix(pred$confusion)
```
#### looking at the confusion matrix i could say our model performs good enough.
