---
title: "Assignment 2"
author: "Prashant Gupta"
Vid: "V01038654"
output: html_document
---

## Problem 4.1


```{r message=FALSE, warning=FALSE}
library(dplyr)
library(esquisse)
library(corrplot)
library(devtools)
library(ggbiplot)
```


#### Loading the Data
```{r}
data= read.csv("Cereals.csv")
```

### A.Which variables are quantitative/numerical? Which are ordinal? Which are nominal?


```{r}
glimpse(data)
```

#### Quantitative Variables
```{r}
print(colnames(select_if(data, is.character)))
```


#### Numeric Variables

```{r}
quancols=(colnames(select_if(data, is.numeric)))
print(quancols)
```

### B.Compute the mean, median, min, max, and standard deviation for each of the quantitative variables. This can be done through R’s sapply() function (e.g., sapply(data, mean, na.rm = TRUE)) or with dplyr.


##### Filtering Numerical Data 

```{r}
quan = select_if(data, is.numeric)
```

#### MEAN

```{r}
sapply(quan,mean, na.rm= TRUE)
```

#### MEDIAN

```{r}
sapply(quan,median, na.rm= TRUE)
```

#### MIN

```{r}
sapply(quan,min, na.rm= TRUE)
```

#### MAX

```{r}
sapply(quan,max, na.rm= TRUE)
```

#### Standard Deviation

```{r}
sapply(quan,sd, na.rm= TRUE)
```

#### C.Use R to plot a histogram for each of the quantitative variables. Based on the histograms and summary statistics, answer the following questions:

#### - Which variables have the largest variability?

#### - Which variables seem skewed?

#### - Are there any values that seem extreme?



```{r warning=FALSE}
library(tidyverse)
ggplot(gather(quan), aes(value)) + geom_histogram(bins = 30L, fill = "#0C6C8A") +
 theme_minimal() +
 theme(plot.title = element_text(hjust = 0.5)) + facet_wrap(~key, scales = 'free_x')
```

```{r}
summary(quan)
```


```{r}
sort(sapply(quan,var, na.rm= TRUE),decreasing = TRUE)
```

##### -Sodium amoungt all Variable has the Highest variablity 

##### -Protein, fat, sodium, fiber, potass, vitamins and Ratings appear to be skewed

##### -In the Vitamins variable we can see that there is a extreme value(25)


#### D.Use R to plot a side-by-side boxplot comparing the calories in hot vs. cold cereals. What does this plot show us? 

```{r}
ggplot(data) +
 aes(x = "", y = calories, colour = type) +
 geom_boxplot(fill = "#112446") +
 scale_color_manual(values = c(C = "#F8766D", 
H = "#FF61C3")) +
 theme_minimal()

```
##### With this plot we can see that there are very less cold cereals (only 2) and there are many hot cereals but they have 7 outliers.


#### E. Use R to plot a side-by-side boxplot of consumer rating as a function of the shelf height. If we were to predict consumer rating from shelf height, does it appear that we need to keep all three categories of shelf height?

```{r}
data$shelf=as.factor(data$shelf)

```

```{r}
ggplot(data) +
 aes(x = "", y = rating, colour = shelf) +
 geom_boxplot(fill = "#112446") +
 scale_color_hue(direction = 1) +
 theme_minimal()


```
##### Althog shelf 3 is right skew but i think we should keep all the shelf.


#### F.Compute the correlation table for the quantitative variable (function cor()). In addition, generate a matrix plot for these variables (function plot(data)).

#### - Which pair of variables is most strongly correlated?

#### - How can we reduce the number of variables based on these correlations?

#### - How would the correlations change if we normalized the data first?

```{r}
corr=cor(quan, method = "pearson")
corrplot(corr, method = "number")
```
##### Weight and calories have the most positive correlation (.70) whereas rating and calories have the most negative correlation (-0.69)


#### G. Consider the first PC of the analysis of the 13 numerical variables in Table 4.11. Describe briefly what this PC represents. 


```{r}
pca=prcomp(na.omit(quan))
summary(pca)
```

```{r}
ggbiplot(pca , varname.size = 2.5)
```


### Problem 4.2

```{r}
data2= read.csv("Universities.csv")
```



```{r}
glimpse(data2)
```

#### A.Remove all categorical variables. Then remove all records with missing numerical measurements from the dataset.

```{r}
quan2 = select_if(data2, is.numeric)
```

```{r}
head(quan2)
```
```{r}
quan2=na.omit(quan2)
```


#### B.Conduct a principal components analysis on the cleaned data and comment on the results. Should the data be normalized? Discuss what characterizes the components you consider key.

```{r}
pca2=prcomp(quan2)
summary(pca2)
```

```{r}
ggbiplot(pca2)
```

