---
title: "Assignment 10 "
author: "Prashant Gupta"
Vid: "V01038654"
output: html_document
---

## Problem 14.4

```{r message=FALSE, warning=FALSE}
library(arules)
library(arulesViz)
```


```{r}
ct.df <- read.csv("Coursetopics.csv")
summary(ct.df)
```

```{r}
ct.mat <- as.matrix(ct.df) # converting to matrix from dataframe
head(ct.mat)
```

```{r}
ct.trans <- as(ct.mat, "transactions")  # converting to "transaction" class
ct.trans@itemInfo
```

```{r}
rules <- apriori(ct.trans, parameter = list(supp = 7/365, conf = 0.6, target = "rules"))
```

```{r}
inspect(sort(rules, by= 'lift'))
```

```{r}
library(tidyverse)
rules.tbl <- inspect(rules)
rules.tbl[rules.tbl$support >= 0.02 & rules.tbl$confidence >= 0.6,] 
``` 


```{r}
plot(rules)  
```

```{r}
itemFrequencyPlot(ct.trans, ylim=c(0.0,0.5))
```


```{r}
mydata <-  read.csv("Universities-1.csv")
head(mydata)
```

## Problem 15.1

### 1. Remove all records with missing measurements from the dataset.

```{r}
mydata_clean <- na.omit(mydata)

library(dplyr)

# print no. of rows and columns in the dataframe
print(paste("No. of rows:", nrow(mydata_clean)))
print(paste("No. of cols:", ncol(mydata_clean)))
```

### 2.For all the continuous measurements, run k-means clustering using Euclidean distance. Make sure to normalize the measurements. How many clusters should we use?


```{r}
categorical_variables <- names(select(mydata_clean,"State","Public..1...Private..2."))
print(categorical_variables)
```
```{r}
continuous_variables <- setdiff(names(which(sapply(mydata_clean, is.numeric))),("Public..1...Private..2."))
print(continuous_variables)
```

```{r}
mydata_normalised <- as.data.frame(scale(mydata_clean[,continuous_variables]))
dist_mat <- dist(mydata_normalised, method = 'euclidean')
hcluster <- hclust(dist_mat, method = "complete")
```

```{r}
# plot the dendogram
plot(hcluster,cex=0.6)
abline(h = 12, col = 'red')

# from the dendogram we select 6 clusters
# draw dendogram with red borders around the 6 clusters
rect.hclust(hcluster, k=6, border="green")
```

```{r}
# coloring the dendogram branches according to cluster
suppressPackageStartupMessages(library(dendextend))
dend_obj <- as.dendrogram(hcluster)
col_dend <- color_branches(dend_obj, h= 12)
plot(col_dend)
```

```{r}
# getting clusters
sub_grp <- cutree(hcluster, k = 6)
# cluster count
table(sub_grp)
```


### 3. Compare the summary statistics for each cluster and describe each cluster in this context (e.g., “Universities with high tuition, low acceptance rate...”).

```{r}
# Adding the clusters to the table in a column named "class"
mydata_clean['class']<-as.factor(sub_grp)
```

```{r}
# grouping the continuous data by 'class' and taking mean (cluster centers)
cluster_table<-aggregate(mydata_clean[continuous_variables],by=mydata_clean['class'],mean)
summary(cluster_table)
```

```{r}
# In this case there are three major clusters i.e. cluster 1, 2 and 3 and three outliers as cluster i.e. cluster 4, 5 
# and 6. We will

# cluster 1: Universities with low tution (both in_state and out_state) and  high acceptance rate.

# cluster 2: Universities with high tution (both in_state and out_state) and low acceptance rate.

# cluster 3: Universities with low in_state tution and high out_state tution and high acceptance rate.
```


### 4. Use the categorical measurements that were not used in the analysis (State and Private/Public) to characterize the different clusters. Is there any relationship between the clusters and the categorical information?

```{r}
# grouping the categorical data by class
cat_cluster_table<- group_by(mydata_clean[categorical_variables],by=mydata_clean['class'])
summary(cat_cluster_table)

# cluster 1
table(mydata_clean$Public..1...Private..2.[mydata_clean$class == 1])
print("Cluster 1 has a comparable number of Private and Public colleges")

# cluster 2
table(mydata_clean$Public..1...Private..2.[mydata_clean$class == 2])
print("Cluster 2 has a majority of Private colleges")

# cluster 3
table(mydata_clean$Public..1...Private..2.[mydata_clean$class == 3])
print("Cluster 3 has a majority of Public colleges")

# all in all, the three clusters have an ample number of Private colleges than Public due to the fact that the 
# dataset has more private colleges as compared to public ones.

# We can infer from cluster 2 that Private colleges has higher tution fees.
```

### 5. What other external information can explain the contents of some or all of these clusters?


```{r}
# Out of the three major clusters, Cluster3 has most number of Full Time undergrads and cluster2 has the least number
# of Full Time undergrads.

# There is a similar trend for Part Time undergrads as that of FUll Time undergrads.
# We can say that the more students choose Public colleges over Private colleges

# add fees is higher in the cluster3 (majority Public colleges) as compared to the clusters having higher number of 
# private colleges.

# graduation rate is the highest for cluster2 i.e. Universities with high tution (both in_state and out_state) and 
# low acceptance rate.

# no. of new students from top 10 and top 25 is highest for cluster2 i.e. Universities with high tution 
# (both in_state and out_state) and low acceptance rate.
```

```{r}